Charity analysis

### 2022-07-18 Shiny/Test/Flexdashboard rows.Rmd
Uploading row-based version - which I think is better.

---
title: "Charity analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
runtime: shiny
---

@@

Column 
-----------------------------------------------------------------------

### Plotly

```{r}
plotlyOutput("plotlyplot")
```

@@

@@

    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })
#---- Plots --------------------------------------------------------------------    
    # creating plots

@@

    output$fancyplot <- renderPlotly(
      ggplotly(fancyplot())
    )
  })
```

>>>>

---
title: "Charity analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

@@

Row 
-----------------------------------------------------------------------

### KPI 2
```{r}
valueBoxOutput("KPI_box2")
```

### KPI 3
```{r}
valueBoxOutput("KPI_box3")
```

### KPI 4
```{r}
valueBoxOutput("KPI_box4")
```

Row
-----------------------------------------------------------------------

### Plotly
```{r}
plotlyOutput("plotlyplot")
```

@@

Row 
-----------------------------------------------------------------------

@@

    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })

  output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })

    output$KPI_box4 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "admin",
        color = "info",
        icon = "fa-random"
      )
    })

#---- Plots --------------------------------------------------------------------    
    # creating plots

@@

  # Creating fancy plotlyplot
    fancyplotly <- reactive({
      ggplotly(fancyplot(), layout(
                                legend = list(
                                orientation = 'h', x = 0.3, y = -0.1, 
                                title = list(text = 'My legend title'))))
    })

    output$fancyplot <- renderPlotly(
      fancyplot()
    )
  })
```
